---
title: "Airbnb Final Project"
author: "Divya Khandke and Adam Ghazzawi"
date: "11/22/2020"
output: html_document
---

```{r setup, include=FALSE}
#######################
#LOADING SET UP PART 1
######################
knitr::opts_chunk$set(echo = TRUE)

root.dir = "https://github.com/amghazzawi/airbnb-predictions"

library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(stargazer)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(dplyr)
library(mapview)
library(jtools)
library(ggmap)
library(RColorBrewer)
library(wesanderson)
library(viridis)
library(broom)
library(rmarkdown)
library(knitr)
library(kableExtra)
```

```{r warning=FALSE, include=FALSE}
#######################
#LOADING SET UP PART 2
######################
mapTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle=element_text(face="italic"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2)
  )
}

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.background = element_rect(fill = "grey80", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}

palette5 <- c("#FFF717", "#E8BC1C", "#FFAE2B",   "#E86E23", "#FF5940")
palette4 <- c( "#53AAEE", "#438AC3", "#306490" , "#1F4363", "#16314B")
               

#Set up quintile breaks for map legends
qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                 c(.01,.2,.4,.6,.8), na.rm=T)
  }
}

q5 <- function(variable) {as.factor(ntile(variable, 5))}

nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <- as.matrix(measureFrom)
  measureTo_Matrix <- as.matrix(measureTo)
  nn <-   
    get.knnx(measureTo, measureFrom, k)$nn.dist
  output <-
    as.data.frame(nn) %>%
    rownames_to_column(var = "thisPoint") %>%
    gather(points, point_distance, V1:ncol(.)) %>%
    arrange(as.numeric(thisPoint)) %>%
    group_by(thisPoint) %>%
    summarize(pointDistance = mean(point_distance)) %>%
    arrange(as.numeric(thisPoint)) %>% 
    dplyr::select(-thisPoint) %>%
    pull()
  
  return(output)  
}
```


```{r, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE, results='hide',fig.keep='all', results='asis'}
#######################
# Data Loading Part 1 
######################
listings <- read_csv("listings.csv")

districts <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=GEBIED_STADSDELEN&THEMA=gebiedsindeling") 

neighborhoods <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=GEBIED_BUURTEN&THEMA=gebiedsindeling")

zipcode4 <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=PC4_BUURTEN&THEMA=postcode")

land_use <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=GRONDGEBRUIK_2017&THEMA=grondgebruik")

student_housing <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=JONGERENSTUDENTENHUISVESTING&THEMA=jongerenstudentenhuisvesting")

overnight <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=OVERNACHTINGSBELEID&THEMA=overnachtingsbeleid")

green_roofs <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=GROENE_DAKEN&THEMA=groene_daken")

parks <- st_read("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=PARKPLANTSOENGROEN&THEMA=stadsparken")

farming <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=STADSLANDBOUW_PUNT&THEMA=stadslandbouw")

maj_streets <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=STADSSTRAAT&THEMA=stadsstraat")

metro_lines <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=TRAMMETRO_LIJNEN_2020&THEMA=trammetro")

metro_stops <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=TRAMMETRO_PUNTEN_2020&THEMA=trammetro")

walkability <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=WALKABILITY&THEMA=walkability")

hist_build <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=HISTORISCHE_BEBOUWING&THEMA=archeologie")

wall_art <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=WANDKUNST&THEMA=wandkunst")

barbecue <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=BBQ&THEMA=bbq")

dog_park <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=HONDEN_SPEELPLAATS&THEMA=honden")

markets <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=MARKTEN&THEMA=markten")

playgrounds <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=SPORT_OPENBAAR&THEMA=sport")

swim <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=ZWEMWATER&THEMA=zwemwater")

monuments <- read_sf("https://maps.amsterdam.nl/open_geodata/geojson.php?KAARTLAAG=MONUMENTEN&THEMA=monumenten")

monuments <- monuments[monuments$Soort %in% c("Beeldhouwkunst", "Bouwwerk", "Bouwblok", "Park Terrein"), ]

```


``` {r}
#######################
# Data Loading Part 2 
######################
neighborhoods.sf <- neighborhoods %>%
  st_as_sf(coords = "geometry", crs = 4326, agr = "constant") %>%
  st_transform('EPSG:28992')

listings.sf  <- listings %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant") %>%
  st_transform(st_crs(neighborhoods.sf))

#######################
# Neighborhood Plot
######################
ggplot() +
  geom_sf(data = neighborhoods.sf, fill = "grey60") +
  geom_sf(data = listings.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .75) +
  scale_colour_manual(values = palette5,
                      labels = qBr(listings.sf, "price"),
                      name = "Nightly Airbnb Price\n(Quintile Breaks)") +
  labs(title="Nightly Airbnb Price, Amsterdam",
       subtitle = "Figure 1") +
  mapTheme()
```


``` {r}
#######################
# District Plot
######################
districts.sf <- districts %>%
  st_as_sf(coords = "geometry", crs = 4326, agr = "constant") %>%
  st_transform('EPSG:28992')

listings.sf  <- listings %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant") %>%
  st_transform(st_crs(districts.sf))

ggplot() +
  geom_sf(data = districts.sf, fill = "black") +
  geom_sf(data = listings.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .75) +
  scale_colour_manual(values = palette4,
                      labels = qBr(listings.sf, "price"),
                      name = "Nightly Airbnb Price\n(Quintile Breaks)") +
  labs(title="Nightly Airbnb Price, Amsterdam",
       subtitle = "Figure 2") +
  mapTheme()
```

``` {r}
#######################
# Zipcode Plot
######################
zipcode.sf <- zipcode4 %>%
  st_as_sf(coords = "geometry", crs = 4326, agr = "constant") %>%
  st_transform('EPSG:28992')

listings.sf  <- listings %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant") %>%
  st_transform(st_crs(zipcode.sf))

ggplot() +
  geom_sf(data = zipcode.sf, fill = "grey50") +
  geom_sf(data = listings.sf, aes(colour = q5(price)), 
          show.legend = "point", size = .75) +
  scale_colour_manual(values = palette4,
                      labels = qBr(listings.sf, "price"),
                      name = "Nightly Airbnb Price\n(Quintile Breaks)") +
  labs(title="Nightly Airbnb Price, Amsterdam",
       subtitle = "Figure 3") +
  mapTheme()
```



```{r install-mapboxapi, eval = FALSE}
#######################
# Mapbox Integration
######################
install.packages("mapboxapi", dependencies = TRUE)
```

```{r install-token, eval = FALSE}
#######################
# Mapbox Tokens
######################
my_token <- "pk.eyJ1IjoiZGtoYW5ka2UiLCJhIjoiY2tnMmI1eDVtMDMwMTJ0cGQwY2NmNGNkNSJ9.kSDKluQUL8p3oIpkX1Qjvg"

library(mapboxapi)
mb_access_token(my_token)

```
* `streets-v11`: [The core Mapbox Streets basemap](https://www.mapbox.com/maps/streets)
* `outdoors-v11`: [A basemap designed for outdoor recreation uses](https://www.mapbox.com/maps/outdoors)
* `light-v10`: [A light, greyscale background suitable for thematic overlay](https://www.mapbox.com/maps/light)
* `dark-v10`: [A dark basemap suitable for thematic overlay](https://www.mapbox.com/maps/dark)
* `satellite-v9`: [A global satellite basemap derived from MODIS, Landsat, & proprietary imagery sources](https://www.mapbox.com/maps/satellite)
* `satellite-streets-v11`: The satellite basemap with a streets overlay


```{r mapbox-map}
#######################
# Mapbox Styling
######################
library(leaflet)
library(mapboxapi)

mapbox_map <- leaflet() %>%
  addMapboxTiles(style_id = "light-v10",
                 username = "mapbox") 

mapbox_map
```

```{r geocode-central amsterdam}
############################
# Mapbox Amsterdam Geocoding
############################
afhaus <- mb_geocode("Westermarkt 20, 1016 GV Amsterdam, Netherlands")

afhaus #takes long lat pair and #tidygeocode package!
```

```{r view-central amsterdam}
#######################
# Mapbox Plot Amsterdam
######################
mapbox_map %>%
  setView(lng = afhaus[1],
          lat = afhaus[2],
          zoom = 12)

```


```{r map-site-neighborhoods map box}
#######################
# Mapbox with Districts
######################
mapbox_map %>%
  addPolygons(data = districts)

```

``` {r}

#Double checking how it looks with Mapview - CAN DELETE

mapview(districts.sf)
```


```{r echo=FALSE, fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
listings %>% 
  dplyr::select(price, neighbourhood, room_type) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_bar(position = "dodge", stat = "summary", fun.y = "mean") +
     facet_wrap(~Variable, ncol = 1, scales = "free") +
     labs(title = "Price as a function of\ncategorical variables", y = "Mean_Price") +
     plotTheme() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
numericVars <- 
  select_if(st_drop_geometry(listings.sf), is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables") 
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
avgneighb_price <- 
  listings.sf %>% group_by(neighbourhood) %>% summarise(meanprice = mean(price))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Airbnb located in city center neighborhoods
citycenterlist <- list("Centrum-Oost",
                        "Centrum-West",
                       "Zuid",
                       "IJburg - Zeeburgereiland",
                       "Oud-Noord",
                       "De Pijp - Rivierenbuurt"
                        )
listings.sf <- listings.sf %>%
  mutate(City_Center = neighbourhood %in% citycenterlist)
listings.sf$City_Center <- ifelse(listings.sf$City_Center == "TRUE", 1, 0)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Airbnb provides entire home to tenant
entirehomelist <- list("Entire home/apt"
                        )
listings.sf <- listings.sf %>%
  mutate(Entire_Home = room_type %in% entirehomelist)
listings.sf$Entire_Home <- ifelse(listings.sf$Entire_Home == "TRUE", 1, 0)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
st_c <- st_coordinates

## Metro Stops
metro_stops.sf <- metro_stops%>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
metro_stops.sf <- st_join(metro_stops.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    metrostops_nn1 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(metro_stops.sf)), 1))

## Metro Lines
metro_lines.sf <- metro_lines%>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
metro_stops.sf <- st_join(metro_lines.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    metrolines_nn3 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(metro_lines.sf)), 3))

## Swimming Areas
swim.sf <- swim%>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
swim.sf <- st_join(swim.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    swim_nn1 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(swim.sf)), 1))


## Wall Art
wall_art.sf <- wall_art%>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
metro_stops.sf <- st_join(wall_art.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    wallart_nn3 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(wall_art.sf)), 1))

## Markets
markets.sf <- markets%>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
markets.sf <- st_join(markets.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    markets_nn1 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(markets.sf)), 1))

## Playgrounds
playgrounds.sf <- playgrounds %>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
playgrounds.sf <- st_join(playgrounds.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    playgrounds_nn2 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(playgrounds.sf)), 2))

## Student Housing
students.sf <- student_housing %>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
students.sf <- st_join(students.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    students_nn2 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(students.sf)), 2))

## Historic buildings
hist_build.sf <- hist_build %>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
hist_build.sf <- st_join(hist_build.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    histbuild_nn3 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(hist_build.sf)), 3))

## Monumuments
monuments.sf <- monuments %>%
  st_transform(st_crs(districts.sf)) %>%
  st_as_sf()
monuments.sf <- st_join(monuments.sf, districts.sf, join = st_intersects, left = FALSE)

listings.sf <-
  listings.sf %>%
  mutate(
    monuments_nn3 = nn_function(st_c(st_centroid(listings.sf)), st_c(st_centroid(monuments.sf)), 3))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
reg1 <- lm(price ~ ., data = st_drop_geometry(listings.sf) %>% 
                                 dplyr::select(price, neighbourhood, availability_365, number_of_reviews, minimum_nights, Entire_Home, markets_nn1, metrostops_nn2, students_nn2, wallart_nn3, playgrounds_nn2, metrolines_nn3, histbuild_nn3, monuments_nn3))

summary(reg1)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#Subset listings dataframe into all homes with listed sale prices
rents <- subset(listings.sf, price > 0)

#Setting up test and training datasets
inTrain <- createDataPartition( 
  y = paste(listings.sf$neighbourhood), 
  p = .70, list = FALSE)

rents.training <- rents[inTrain,] 
rents.test <- rents[-inTrain,]  

#Multivariate regression
reg.training <- lm(price ~ ., data = st_drop_geometry(rents.training) %>% 
             dplyr::select(price, neighbourhood, availability_365, number_of_reviews, minimum_nights, Entire_Home, markets_nn1, metrostops_nn2, students_nn2, wallart_nn3, playgrounds_nn2, metrolines_nn3, histbuild_nn3, monuments_nn3))

stargazer(
  reg.training,
  type = "text",
  title = "Linear Model Summary Table",
  dep.var.caption = " ",
  dep.var.labels = "Model Features")
```


